--- 
title: "Mathematics for Deep Learning and Artificial Intelligence"
author: "Christian Ramsey & Haohan Wang"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: https://github.com/dyadxmachina/maths-for-deep-learning-ai
url: 'http\://dyadxmachina.com/math-for-deep-learning-and-ai'
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

Placeholder



<!--chapter:end:index.Rmd-->

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-intro.Rmd-->

# Literature

Here is a review of existing methods.

<!--chapter:end:02-literature.Rmd-->

# Methods

We describe our methods in this chapter.

<!--chapter:end:03-method.Rmd-->

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

## Example two

<!--chapter:end:04-application.Rmd-->

# Final Words

We have finished a nice book.

<!--chapter:end:05-summary.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:06-references.Rmd-->


# Introduction 

Placeholder


## R Markdown
## Including Plots
## Why Mathematics 

<!--chapter:end:hw_intro_draft.Rmd-->


# Philosophical Root

Placeholder



<!--chapter:end:introduction_draft_hw.Rmd-->

---
title: "Propositional Logic"
author: "hw"
date: "October 26, 2018"
output: html_document
---
> History of Propositional Logic 

#  Aristotle to George Boole 
* Logic was developed by Aristotle (384-322 BCE). Basically, Aristotles system of logic introduced hypothetical syllogism, temporal model logic and the inductive logic. 

## Branches of logics: 
1. Classical Logic - Aristotelian logic 
2. Symbolic Logic - Mathematical logic 

* Common Ground
"model symbolic logic is a development of the concepts and techniques which were implicit in the work of Aristotle.." - Bassoon and O'conner

In a sense, it agress that the modern symboloic logic is just a development and the extension of the concepts and techniques of Aristotlian logic. 

## Next Moves
### G.W Leibnitz (1646-1716)

He put forward a 2 fold plan that helped reform the logic. 
1. He suggested the establishment of a universal basic ideograms, in which all the scientific concepts could be represented by a combination of basic ideograms. 
2. he also suggested that a unversial calculus of reasoning could be devised which would provide an automatic method of solution for all problems which could be expressed in the universal language. 

### George Boole (1815-1864)
He formulated a system of algebra. Boole applied his algebra to several branches of logic including the syllogism of the classical logic. 
In turn, he showed that the Aristotelian syllogism which had been regarded as practically co-extensive with deductive logic could be shown to be a special case of kind of logical algebra.

> Propositional Logic 


# Definition: it is the most basic branch of mathematical logic. It is also called propositional calculus (PC)

<!--chapter:end:logic_hw.Rmd-->

