--- 
title: "Mathematics for Deep Learning and Artificial Intelligence"
author: "Christian Ramsey & Haohan Wang"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: https://github.com/dyadxmachina/maths-for-deep-learning-ai
url: 'http\://dyadxmachina.com/math-for-deep-learning-and-ai'
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

Placeholder



<!--chapter:end:index.Rmd-->

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-intro.Rmd-->

# Literature

Here is a review of existing methods.

<!--chapter:end:02-literature.Rmd-->

# Methods

We describe our methods in this chapter.

<!--chapter:end:03-method.Rmd-->

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

## Example two

<!--chapter:end:04-application.Rmd-->

# Final Words

We have finished a nice book.

<!--chapter:end:05-summary.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:06-references.Rmd-->


# Introduction 

Placeholder


## R Markdown
## Including Plots
## Why Mathematics 

<!--chapter:end:hw_intro_draft.Rmd-->


# Philosophical Root

Placeholder



<!--chapter:end:introduction_draft_hw.Rmd-->

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:logic_fz.Rmd-->

